Trends of SDR in Thessaloniki

### 2023-05-25 Article.Rmd
Commit 2023-05-16 14:17
Commit 2023-05-25 13:17

---
title:         "Trends of SDR in Thessaloniki"
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
link-citations: yes
colorlinks:     yes
urlcolor:       blue
bibliography:   [references.bib]
biblio-style:   apalike
date:           "`r format(Sys.time(), '%F')`"

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}
  - \usepackage{setspace}\doublespacing
  - \usepackage{float}

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        no
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5

---

```{r echo=F, include=T}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

The shortwave downward solar irradiance (SDR) at the Earth's surface plays s significant role, on the climate.
Changes of the SDR can be related to major changes on the factors affecting the radiative forcing balance.
In this study we examine the trends of SDR with the ground-based measurements at Thessaloniki for the period 1993 - 2023.

@@

\FloatBarrier

>>>>

---
title:         "Trends of SDR in Thessaloniki"

# documentclass:  article
# classoption:    a4paper,oneside
# fontsize:       12pt
# geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
# link-citations: yes
# colorlinks:     yes
# urlcolor:       blue
# bibliography:   [references.bib]
# biblio-style:   apalike
# date:           "`r format(Sys.time(), '%F')`"
# 
# header-includes:
#   - \usepackage{caption}
#   - \usepackage{placeins}
#   - \captionsetup{font=small}
#   - \usepackage{setspace}\doublespacing
#   - \usepackage{float}

author:
  - name:        Natsis Athanasios
    email:       natsisphysicist@gmail.com
    affiliation: Laboratory of Atmospheric Physics, AUTH
    correspondingauthor: true
    footnote: 1
  - name:        Alkiviadis Bais
    email:       bob@example.com
    affiliation: Another University
address:
  - code: Some Institute of Technology
    organization: Big Wig University
    addressline: 1 main street
    city: Gotham
    state: State
    postcode: 123456
    country: United States
  - code: Another University
    organization: Department
    addressline: A street 29
    postcode: 2054 NX
    city: Manchester,
    country: The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

  It consists of two paragraphs.
keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: references.bib
linenumbers: false
numbersections: true

output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        no
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
---

```{r echo=F, include=T}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!ht'   )
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

The shortwave downward solar irradiance (SDR) at the Earth's surface plays s significant role, on the climate.
Changes of the SDR can be related to major changes on the factors affecting the radiative forcing balance.

In this study we examine the trends of SDR with the ground-based measurements at Thessaloniki for the period 1993 - 2023.

@@

<!-- \FloatBarrier -->
